\documentclass[margin,line]{res}
\usepackage{hyperref}
\usepackage{comment}
\pagestyle{plain}

    %%%%%%%%%%%%%%%%%%2%%%%%%%%%%%
    \oddsidemargin  -.2in
    \evensidemargin -.2in
    \textwidth      5.5in   %letter:6.5 A4: 6.0
    \textheight     9.0in
    \headheight     0.0in
    \topmargin      0.0in
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}
\newenvironment{list3}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.3in}}}{\end{list}}

\makeatletter
\renewenvironment{thebibliography}[1]
     {\list{\@biblabel{\@arabic\c@enumiv}}%
           {\settowidth\labelwidth{\@biblabel{#1}}%
            \leftmargin\labelwidth
            \advance\leftmargin\labelsep
            \@openbib@code
            \usecounter{enumiv}%
            \let\p@enumiv\@empty
            \renewcommand\theenumiv{\@arabic\c@enumiv}}%
      \sloppy
      \clubpenalty4000
      \@clubpenalty \clubpenalty
      \widowpenalty4000%
      \sfcode`\.\@m}
     {\def\@noitemerr
       {\@latex@warning{Empty `thebibliography' environment}}%
      \endlist}
\makeatother
\begin{document}

\name{Seungyeop Han \vspace*{.1in}}

\begin{resume}

%%%%%%%%%%%%%%%%%%%%%%%% Personal %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\sc Contact Information}
\vspace{.05in}

\begin{tabular}{@{}p{3in}p{3in}}
Ph.D Student @ \textbf{CSE.UW}                & Computer Science \& Engineering,\\
{\it Email:} syhan@cs.washington.edu		  &University of Washington    \\
{\it Web:} \url{http://cs.washington.edu/homes/syhan}	  & Box 352350 Seattle WA 98195-2350   \\
\end{tabular}

%%%%%%%%%%%%%%%%%%%%%%%%%% Interests %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\sc Research Interests}
%Distributed Systems, Computer Networking, Peer-to-peer Computing, \\ Operating Systems, World Wide Web, Privacy, Security
My research interests are primarily in mobile computing and networked systems. 
It spans topics like computer networking, mobile systems, operating systems, privacy and security. 
Recently, I have worked on various project in mobile systems: 
system for continuous high datarate perception~\cite{pa14, hotos13}, 
natural language interface for third-party mobile applications~\cite{ubicomp13, hotmobile13}, 
and studying and providing solutions for smartphone privacy
issues~\cite{ccs14,sec14,tocs14,spsm12,nsdi12,ccs2011}).  
Also I have participated in projects to create new Internet architectures for
finer grained identity control in IPv6~\cite{sigcomm13} and censorship
resistant property~\cite{hotnets11}.  Prior to studying in UW, I participated
in various research projects, such as GPU-accelerated SSL~\cite{nsdi11}, 
and online social network analysis~\cite{www07}.


%%%%%%%%%%%%%%%%%%%%%%%%%% Education %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\sc Education}
University of Washington, WA \\
\vspace*{-.1in}
\begin{list1}
\item[] Ph.D. in Computer Science and Engineering (GPA 3.86/4.0) \hfill{\it Sep. 2010 -- }
\item[] (\textit{Advisors}: David Wetherall, Arvind Krishnamurthy)
\item[] M.S. in Computer Science and Engineering\hfill{\it Mar. 2012}
%\item[] \textit{Quals Project}: Tracking the Trackers: A Study of Third-Party Tracking by Mobile Apps in the Wild (\textit{Advisor}: David Wetherall, Jaeyeon Jung) 
\end{list1}


KAIST, Korea  \\
\vspace*{-.1in}
\begin{list1}
\item[] M.S. in Division of Computer Science (GPA 4.15/4.3) \hfill{\it Feb. 2007}
\item[] \textit{Thesis}: Analysis of Blog Spams and Collaborative Blog Spam Filtering Using Adaptive Percolation Search (\textit{Advisor}: Sue B. Moon)
\item[] 
\item[] B.S. in Division of Computer Science with a minor in Dept.~of Mathematics \hfill{\it Feb. 2005}
\item[] \textit{Summa Cum Laude}, (GPA 3.92/4.3)
\item[] Studied Summer 2003 at University of California, Berkeley. 
\end{list1}

%University of California at Berkeley, CA, USA \hfill {\it Jun. 2003 -- Aug. 2003}\\
%\vspace*{-.1in}
%\begin{list1}
%\item[] GPA 3.85/4.0
%\item[] Completed courses in summer session: Machine Structure, Discrete Mathematics
%\end{list1}

%Gyeonggi Science High School, Korea \hfill{\it Mar. 1999 -- Feb. 2001}\\
%\vspace*{-.1in}
%\begin{list1}
%\item[] Graduated one year early 
%\end{list1} 


%%%%%%%%%%%%%%%%%%%%%%%%%   Publications   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\sc Publications}
\nocite{*}
\bibliographystyle{plainyr-rev}
\bibliography{mypapers}

\begin{comment}
\section{\sc Working Papers}
\begin{thebibliography}{10}
%\bibitem{taintdroid}
%William Enck, Peter Gilbert, \textbf{Seungyeop Han}, Vasant Tendulkar, Byung-Gon Chun,
%  Landon~P. Cox, Jaeyeon Jung, Patrick McDaniel, and Anmol~N. Sheth.
%\newblock Taintdroid: An information-flow tracking system for realtime privacy
%  monitoring on smartphones.
%\newblock Under Submission.
\bibitem{toip2}
Haewoon Kwak, \textbf{Seungyeop Han}
\newblock So Many Bad Guys, So Little Time: Exploring Crowdsourcing Frameworks for Combating Toxic Players in Online Games.
\newblock Under Submission.

\bibitem{toip2}
Vincent Liu, \textbf{Seungyeop Han}, Adam Lerner, Arvind Krishnamurthy, Thomas Anderson. 
\newblock Internet Privacy by Construction. 
\newblock Tech Report UW-CSE-12-09-04, 2012.


\bibitem{applog}
\textbf{Seungyeop Han}, Jaeyeon Jung, and David Wetherall.
\newblock A study of third-party tracking by mobile apps in the wild.
\newblock Tech Report UW-CSE-12-03-01, 2012.

\end{thebibliography}
\end{comment}

\section{\sc Patents}
Yun-Cheng Ju, Matthai Philipose, \textbf{Seungyeop Han}. \\
Facilitating development of a spoken natural language interface. \\
US Patent Application \#20140244254, Submitted. 

Young Su Ko, \textbf{Seungyeop Han}, Jung Woo Seo. \\
System and Method for Collecting Document. \\
US Patent Application \#20110320427, Submitted. 

\section{\sc Teaching Expereiences}
Seminar Coordinator, University of Washington \hfill{\it Sep. 2014 -- Present} \\
Networks Seminar (CSE590L)

Teaching Assistant, University of Washington \hfill{\it Sep. 2010 -- Dec. 2010} \\
Network Systems (CSEP561)

Teaching Assistant, KAIST \hfill{\it Mar. 2005 -- Feb. 2007} \\
Introduction to Computer Networking (CS441), Special Topics in Computer Science - Wireless and Mobile Computing (CS492), Introduction to Computer Programming (CS101)
%{\em Research Assistant} \hfill {\bf August, 2003 -- }\\
%{\em Graduate Student} \hfill {\sc March, 2005 -- present}\\
%Includes current M.S. research, courseworks, and managing projects.
%A short summary of my research activities at KAIST and elsewhere begins on page 3.
%{\em Teaching Assistant} \hfill {\sc Mar. 2005 -- Feb. 2007}\\
%Worked as a TA for three courses, Introduction to Computer Networking, Special Topics in Computer Science - Wireless and Mobile Computing, and Introduction to Computer Programming. Assisted in design of homework assignments and lab experiments; graded homework and exams; and provided office hours. First two courses were taught in English.


%%%%%%%%%%%%%%%%%%%%%%%%%%%% PROFESSIONAL EXPERIENCE %%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\sc Work Experiences}
{\bf Google Inc.} (Google[x]), Mountain View, CA \\
{\em Intern} \hfill {\it Jun. 2014 -- Sep. 2014} \\

{\bf Telefonica I+D}, Barcelona, Spain \\
{\em Research Intern} \hfill {\it Apr. 2013 -- Jul. 2013} \\
Worked on application migration between smartphones and computers. 
I explored the design for migration platform with FirefoxOS phones.

{\bf Microsoft Research} (Mobile \& Networking Research Group), Redmond, WA \\
{\em Contracted Researcher} via Nytec Inc. \hfill {\it Oct. 2012 -- Mar. 2013} \\
{\em Research Intern} \hfill {\it Jun. 2012 -- Sep. 2012} \\
Worked on NLify project, which enables third party smartphone applications to
interact users via spoken natural language. I designed and implemented
development supporting tools well integrated with Visual Studio, and workflow
including specifying spoken language usages, amplifying them, and converting
into Windows Phone application control.

{\bf Forward Ventures LLC.}, Seoul, Korea \\
{\em Software Dev Lead} \hfill {\it Aug. 2010 -- Sep. 2010} \\
Architected and developed a social commerce website,
\url{http://coupang.com}. 
%Until the launching, I was the only developer, thus managed the whole system.

{\bf NHN Corp.}, Korea \\
{\em Software Engineer, Open UI Tech. Team} \hfill {\it Sep. 2009 -- Aug. 2010}\\
Developed an open source web site builder, XpressEngine.

{\em Software Engineer, P2P Platform Development Team} \hfill {\it Feb. 2007 -- Sep. 2009}\\
Developed P2P platform libraries. %, for both parts of linux servers and windows clients.
The main component of the libraries was a P2P connector enabling applications to establish reliable connections between peers. 
In addition, I participated in designing systems and algorithms for optimal peer
selection, P2P livecast and VoD service.

{\bf Microsoft Research Cambridge}, UK \\
{\em Research Intern} \hfill {\it Sep. 2006 -- Dec. 2006} \\
Designed and evaluated spatial sampling algorithms for end-system network monitoring in enterprise network by exploiting existence of heavy-hitters. 
%A short summary of my research activities at KAIST and elsewhere begins on page 3.

%{\em System Administrator} \hfill {\sc Mar. 2005 -- Feb. 2007}\\
%Set up and administrated linux servers including main server for HTTP, mail, samba, and analysis servers in my lab. 

%{\bf KISTI} \hfill{\bf Daejeon, Korea}\\
%{\em Part Time Programmer} \hfill {\sc Jul. 2005 -- Aug. 2005}\\
%As a part-time programmer, I had working experience at Grid Research Team of KISTI Super Computing Center.
%I helped developing Data Grid system with Python and Java.

{\bf Tmax Soft}, Korea\\
{\em Summer Intern} \hfill {\sc Jul. 2004 -- Aug. 2004}\\
Developed XML Schema Navigator (in Java), capable of dynamic XML node creation.\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  TALKS   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%% Honors and Awards %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\sc Honors and Awards} 
\begin{list2}
\item{Doctoral Study Abroad Scholarship, The Korea Foundation for Advanced Studies (KFAS), Sep. 2010 -- Jun. 2015 }
\item{Honorable Mention Award~\cite{ubicomp13}, Ubicomp, 2013}
\item{Best Poster Award~\cite{sigcomm10}, SIGCOMM, 2010}
\item{Outstanding master's thesis, CS division, KAIST, 2007}
\item{\textit{Summa Cum Laude}, KAIST, 2005}
\item{Honorable Mention in commendation for the outstanding paper~\cite{icat04}, ICAT, 2004}
%\item{Tuition Waived - Scholarship by Government, KAIST, 2001--2004(BS), 2005--2006(MS) }
\item{Kim, Younghan Global Leader Scholarship, KAIST, 2002--2004}
\end{list2}



%\vspace*{-2.5mm}
%\vspace*{-.1in}

%\section{\sc Skills}
%{\bf Programming Langugages} : C/C++/C\#/Objective-C, JAVA, PHP, Python, MATLAB\\
%{\bf Operating Systems} : Unix/Linux, Windows, MacOS\\
%{\bf Spoken Languages} : 
%\begin{list1}
%\item[]{Korean : Native}
%\item[]{English : Fluent, TOEFL IBT 108/120 (Jun.~2009)}
%\end{list1}

\section{\sc Services}
\begin{list2}
\item{Reviewer: Ubicomp (2014), MC$^2$R (2013)}
\item{PC Member: ACM S3 Workshop (2013)} 
\end{list2}


\section{\sc Other Activities}
\begin{list2}
\item{Graduate Admission Committee, Computer Science \& Engineering, University of Washington, 2014--2015}
\item{Commiter, XpressEngine (\url{http://xpressengine.org/}), 2007--2010 }
%\begin{list1}
%\item[] {I have contributed to many parts of XE project, which is the most popular PHP-based website building framework in South Korea.}
%\end{list1}
\item{Class representative for the class of 2005, Division of Computer Science, KAIST, 2004}\\
%\item{Administrator of a telnet-based BBS system, BAR, in KAIST, 2003--2004}
%\begin{list1}
%\item[]{BAR is a BBS system with more than 1000 users at KAIST{}. I worked as an administrtor of BAR and 
%developed new features.}\\
%\end{list1}
%\item{Member of a linux club, Kaist Linuxers (KALI), at KAIST, 2003--2004}
%\begin{list1}
%\item[]{As a member of KALI, I provided Linux seminars and participated to devlope several systems on Linux. In particular, 
%I developed a P2P audio streaming player, Kali Audio Streaming Service in 2004, and exhibited it at 
%the first IT-Festival sponsored by Samsung SDS{}.}\\
%\end{list1}
%\item{Member of a pop chorus club, MUSE, at KAIST, 2001--2004}
%\begin{list1}
%\item[]{KAIST MUSE is a pop-chorus club, which has more than sixty members. It puts on two performances a year in May and November. I served as an organization chair whose tasks include securing a concert hall and audio/video systems; and getting sponsorships; and printing and distributing posters and brochures.}
%\end{list1}
\end{list2}
%\vspace{2in}
\section{\sc References}
Available upon requests.
%\vspace{.05in}
\begin{comment}
\begin{tabular}{@{}p{3in}p{3in}}
{\bf Prof. David Wetherall} & {\bf Dr. Jaeyeon Jung} \\
{\em Computer Science and Engineering} & \\
University of Washington & Microsoft Research \\
{djw@cs.washington.edu} & {jjung@microsoft.com} \\
\\
{\bf Prof. Arvind Krishnamurthy} & {\bf Dr. Matthai Philipose} \\
{\em Computer Science and Engineering} &  \\
University of Washington & Microsoft Research \\
{arvind@cs.washington.edu} & {matthaip@microsoft.com}

\end{tabular}
\end{comment}
%\end{comment}
%%% LIST UP WHAT DID YOU DO
\end{resume}

\end{document}

